The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-18 paper/Analisis.tex
New off-center profile  plot
minor changes

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ where
$R$ is the radii of the homogeneous sphere and 
we choose two spheres in each side of the $\hat{\textbf{x}}$ axis
two at $0.25 R$ and the other two at $0.5 R$.

@@

But with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle
in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
galaxies are oriented in random directions which implies that off-center emission
is not going to be observed in all the observed galaxies.

@@

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
are shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are most sensitive to the effect of rotation.

@@

>>>>

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ where
$R$ is the radii of the homogeneous sphere and 
we choose two spheres in each side of the $\hat{\textbf{x}}$ axis,
two at $\mp 0.25 R$ and the other two at $\mp 0.5 R$.

@@

In the case of the Off-center model the 
%But with the set up of the off-center models
%where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
%located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
%off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
%represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
%the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
%with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
%show exactly the same trend. We find a high dependency in the viewing angle
%in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
%at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
%galaxies are oriented in random directions which implies that off-center emission
%is not going to be observed in all the observed galaxies.

@@

The outgoing spectra for two different spheres located at $\pm 0.5R$ 
are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
the resulting profiles show more interesting morphologies than in the
$\pm 0.25R$ case.

@@

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{Off-center distribution $\mathrm{Ly}\alpha$ profiles, 
off-center positions.
   \label{fig:OC_profiles}} 
\end{figure*}
